\chapter{Advanced Computer Graphics}
\label{chap:advanced_computer_graphics}

	\firstletter{C}hapter 3 introduced fundamental concepts of computer graphics.
	A major topic in that chapter was how to represent and render geometry using surface primitives such as points, lines, and polygons.
	In this chapter our primary focus is on volume graphics.
	Compared to surface graphics, volume graphics has a greater expressive range in its ability to render inhomogeneous materials, and is a dominant technique for visualizing 3D image (volume) datasets.
	
	We begin the chapter by describing two techniques that are important to both surface and volume graphics.
	These are simulating object transparency using simple blending functions, and using texture maps to add realism without excessive computational cost.
	We also describe various problems and challenges inherent to these techniques.
	We then follow with a focused discussion on volume graphics, including both object-order and image-order techniques, illumination models, approaches to mixing surface and volume graphics, and methods to improve performance.
	Finally, the chapter concludes with an assortment of important techniques for creating more realistic visualizations.
	These techniques include stereo viewing, antialiasing, and advanced camera techniques such as motion blur, focal blur, and camera motion.

\section{Transparency and Alpha Values}

	Up to this point in the text we have focused on rendering opaque objects — that is, we have assumed that objects reflect, scatter, or absorb light at their surface, and no light is transmitted through to their interior. Although rendering opaque objects is certainly useful, there are many applications that can benefit from the ability to render objects that transmit light. One important
	application of transparency is volume rendering, which we will explore in greater detail later in the chapter.

\section{Texture Mapping}

	Texture mapping is a technique to add detail to an image without requiring modelling detail. Texture mapping can be thought of as pasting a picture to the surface of an object. The use of texture mapping requires two pieces of information: a \emph{texture map} and \emph{texture coordinates}. The texture map is the picture we paste, and the texture coordinates specify the location where the picture is pasted. More generally, texture mapping is a table lookup for color, intensity, and/or transparency that is applied to an object as it is rendered. Textures maps and coordinates are most often two-dimensional,
	but three-dimensional texture maps and coordinates are supported by most new graphics hardware.

\section{Volume Rendering}
\label{sec:volume_rendering}

	Until now we have concentrated on the visualization of data through the use of geometric primitives such as points, lines, and polygons.
	For many applications such as architectural walk-throughs or terrain visualization, this is obviously the most efficient and effective representation for the data.
	In contrast, some applications require us to visualize data that is inherently volumetric (which we refer to as 3D image or volume datasets).
	For example, in biomedical imaging we may need to visualize data obtained from an MR or CT scanner, a confocal microscope, or an ultrasound study.
	Weather analysis and other simulations also produce large quantities of volumetric data in three or more dimensions that require effective visualization techniques.
	As a result of the popularity and usefulness of volume data over the last several decades, a broad class of rendering techniques known as volume rendering has emerged. The purpose of volume rendering is to effectively convey information within volumetric data.
	\section{3D Widgets and User Interaction}
	\label{sec:3dwui}
	Chapter 3 provided an introduction to interaction techniques for graphics (see ``Introducing vtkRenderWindowInteractor'' on page \pageref{pg:rwi} ).
	In the context of visualization, interaction is an essential featureof systems that provide methods for data exploration and query. The classes
	vtkRenderWindowInteractor and vtkInteractorStyle are core constructs used in VTK to capturewindowing-system specific events in the render window, translate them into VTK events, and then take action as appropriate to that event invocation.
	In Chapter 3 we saw how these classes could be used to manipulate the camera and actors to interactively produce a desired view. This functionality,
	however, is relatively limited in its ability to interact with data. For example, users often wish tointeractively control the positioning of streamline starting points, control the orientation of a clipping plane, or transform an actor. While using interpreted languages (see ``Interpreted Code'' on page \pageref{pg:rwi} ) can go a long way to provide this interaction, in some situations the ability to see what you are doing when placing objects is essential. Therefore, it is apparent that a variety of user interaction techniques is required by the visualization system if it is to successfully support real-world applications.

\section{Bibliographic Notes}
	
	Color mapping is a widely studied topic in imaging, computer graphics, visualization, and human factors. References \cite{Durrett87} \cite{Ware88} \cite{Rheingans92} provide samples of the available literature. You also may want to learn about the physiological and psychological effects of color on perception. The text by Wyszecki and Stiles \cite{Wyszecki82} serves as an introductory reference.
	
	Contouring is a widely studied technique in visualization because of its importance and popularity. Early techniques were developed for 2D data \cite{Watson92}. Three-dimensional techniques were developed initially as contour connecting methods \cite{Fuchs77} --- that is, given a series of 2D contours on evenly spaced planes, connect the contours to create a closed surface. Since the introduction of marching cubes \cite{Lorensen87}, many other techniques have been implemented. (A few of these include \cite{Nielson91} \cite{Montani94} and \cite{Durst88} ). A particularly interesting reference is given by Livnat et al. \cite{Livnat96}. They show a contouring method with the addition of a preprocessing step that generates isocontours in near optimal time.
	
	Although we barely touched the topic, the study of chaos and chaotic vibrations is a delightfully interesting topic. Besides the original paper by Lorenz \cite{Lorenz63}, the book by Moon \cite{Moon87} is a good place to start.
	
	Two- and three-dimensional vector plots have been used by computer analysts for many years \cite{Fuller80}. Streamlines and streamribbons also have been applied to the visualization of complex flows \cite{Volpe89}. Good general references on vector visualization techniques are given in \cite{Helman90} and \cite{Richter90}.
	
	Tensor visualization techniques are relatively few in number. Most techniques are glyph oriented \cite{Haber90} \cite{deLeeuw93}. We will see a few more techniques in Chapter 9.
	
	Blinn \cite{Blinn82}, Bloomental \cite{Bloomenthal88} \cite{Bloomenthal97} and Wyvill \cite{Wyvill86} have been important contributors to implicit modeling. Implicit modeling is currently popular in computer graphics for modeling "soft" or "blobby" objects. These techniques are simple, powerful, and are becoming widely used for advanced computer graphics modeling.
	
	
	\printbibliography
	
	
	\section{Exercises}
	